\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usepackage{geometry}
\geometry{
    letter, 
    portrait, 
    margin=0.5in
}

\pagenumbering{gobble}

\usepackage{multicol}
\setlength{\columnsep}{0.8cm}
 
\title{Thavy Thach Resume}
\author{Thavy Thach}
\date{December 2020}
 
\begin{document}
\textbf{{\huge Thavy Thach}}\quad{\footnotesize{thavythach@gmail.com | 253.844.5812 | \textbf{linkedin/github}: thavythach | \textbf{website}: https://thavy.tech}}
\newline
\noindent\rule{19cm}{0.1pt}

\begin{multicols}{2}

\section*{\underline{Professional Experience} {\small(Selected)}}

{\footnotesize{\textbf{Software Engineer} | IBM / 01-27-20 | Present}}
{\footnotesize{
% \newline\textbf{Cognitive \& Analytics Software Engineer}
\begin{itemize}
	\item[--] Designed and developed \textbf{Angular} reporting tools and DevOps processes that proved to minimize bottlenecks in our client's international supply chain delivery schedule.
	%\item[--] Introduced methodologies and best practices that enhanced product definition, release processes and customization of applications to user needs.
	\item[--] Facilitated customization of systems by encouraging agile development team to adopt emerging standards, like \textbf{Java}, \textbf{Spring MVC}, \textbf{git flow}, and \textbf{Test Driven Development}, resulting in a 15\% decrease in defects.
	\item[--] Architecting \textbf{Angular} predictive mainteance application to support next generation logistical mainteance for the US ARMY, resulting in vehicle mainteance schedules being reduced by 200\%.  
\end{itemize}
}}
\hfill \break
{\footnotesize{\textbf{Computer Scientist} | Missile Defense / 07-22-19 | 12-20-19}}
{\footnotesize{
% \newline\textbf{Cleared Software Guru in Defense \& Space}
\begin{itemize}
	\item[--] Implemented a dynamic reporting tool to drive better Interface Control Document (ICD) and requirement decisions which reduced manual labor lookup by 100\%.
	\item[--] Independently optimized the database design of the Nation's Battle Communications' database providing an improved normalized relational mapping.
\end{itemize}
}}
\hfill \break
{\footnotesize{\textbf{Data Engineering Intern} | Suplari / 02-05-19 | 05-04-19}}
{\footnotesize{
% \newline\textbf{Architecting Custom Insights as a Package}
\begin{itemize}
	\item[--] Substituted generic SSH login credentials with \textbf{AWS} IAM user system and \textbf{Terraform} to provide verbose logging \& increase efficiency internally.
	% \item[--] Worked with key leaders on ”insights” for 15+ customers through Python data wrangling and analysis.
	% \item[--] Developed Predictive insights that leverage AI technologies to find predictive information about a company's financial statements.
	\item[--] Devised 15 master \textbf{PostgreSQL} queries, resulting in a set of packages customers can choose from to determine industry valued insights.
\end{itemize} 
}}
\hfill \break
{\footnotesize{\textbf{Data Scientist Intern} | Honeywell / 06-25-18 | 08-31-18}}
{\footnotesize{
% \newline\textbf{Design \& Analysis of the Aerospace E-Commerce Platform}
\begin{itemize}
	\item[--] Delivered a labor visualization dashboard utilizing \textbf{R} and \textbf{Tableau} that easily identified~\$2.2M in opportunity where the Honeywell team can eliminate unnecessary spend. 
	\item[--] Designed and developed a new \textbf{Android} application that supports high-volume self-service traffic representing~\$500K in annual operational savings.
\end{itemize}
}}
\hfill \break
{\footnotesize{\textbf{Mixed Reality Intern} | HITLabNZ / 04-23-18 | 06-22-18 }}
{\footnotesize{
% \newline\textbf{Superimposition object prototyping in the real-world}
\begin{itemize}
	\item[--] Successfully launched a \textbf{mixed reality} mobile tour guide solution that attracted hundreds of Product Design Students.
	% \item[--] Developed 7 C\# scripts using Unity and Vuforia SDK.
	\item[--] Designed and developed software pipelines involving \textbf{Android}, \textbf{iOS}, and \textbf{Head-Mount Display Devices}.
	% \item[--] Managed high-level decisions regarding budgetary and implementation details, such as: buying a \$500 software license.
\end{itemize}
}}
%\hfill \break
%{\footnotesize{\textbf{Data Scientist Intern II} | Suplari / 12-17-17 | 01-19-18}}
%{\footnotesize{
%\newline\textbf{Developing Machine Learning Solutions at Scale}
%\begin{itemize}
%	\item[--] Wrote Transaction Categorization classification solutions producing 99\% accuracy correspondence.
	% \item[--] Applied Python Scikit-Learn machine learning library to respond to feature detection and tuning of models.
%	\item[--] Reduced Sales Analyst workload by 90\% by developing a multi-classification solution on datasets ranging from 50K to 1.5M rows.
%\end{itemize}
%}}
\hfill \break
{\footnotesize{\textbf{Data Scientist Intern} | Suplari / 05-15-17 | 08-18-17}}
{\footnotesize{
% \newline\textbf{Stealth Startup classification problem solver}
\begin{itemize}
	% \item[--] Collaborated with the Director of Data Science on vendor normalization classification problem on the design, pipeline, and backend levels. 
	\item[--] Leveraged tools like \textbf{Python}, \textbf{Scikit-learn}, \textbf{Pandas}, \textbf{ElasticSearch} in conjunction with machine learning algorithms to improve vendor normalization algorithm.
	\item[--] Developed 8 mathematical models to predict whether given domain is directory or website, impacting master supplier mappings across several customers.
	% \item[--] Led a team of freelance data scientists to coordinate tasks related to ground truth and normalization.
	\item[--] Reduced Sales Analyst workload by 90\% by developing a multi-classification solution on datasets ranging from 50K to 1.5M rows.
\end{itemize}
}}
\hfill \break
{\footnotesize{\textbf{Junior Developer Intern} | DevHub / 05-15-16 | 08-26-16}}
{\footnotesize{
% \newline\textbf{Engineering A Private-Label Web Platform Experience}
\begin{itemize}
	\item[--] Fueled additional revenue stream through responsive customer support, generating \$30k in new license sales. 
	%\item[--] Introduced 3 Django Management Functions in Python as optimizations using the power of MySQL.
	% \item[--] Designed and implemented dynamic repository web zone across all private labels using Zendesk API.
	\item[--] Designed and implemented dynamic repository web zone across all customers powered by the \textbf{Zendesk API}, \textbf{Python}, \textbf{Django}, and \textbf{MySQL}, 
	% \item[--] Implemented new reusable middleware to fix multiple redundancies with global ip configurations.
	% \item[--] Patched 17 customer facing bugs.
\end{itemize}
}}
\section*{\underline{Demonstrated Skills}}
{\footnotesize{
AWS, Python, Java, Git, Bash, Flask, Android, HTML, JavaScript, TypeScript, C, C++, C\#, Django, SciKit-Learn, Angular, React, Laravel, Node.JS, Unity, MySQL, SQLite3, MongoDB, Spring MVC, Oracle, Bamboo, Docker, Go.
}}
\hfill
\hfill \break
\section*{\underline{Project Experience} {\small(Selected)}}
{\footnotesize{\textbf{OutBox | 2020} (Not Published)}}
{\footnotesize{
\newline\textbf{Role:} Architect, Software Engineer
% \newline\textbf{Next Generation Email Service}
\begin{itemize}
	\item[--] A Google inspired email service made in \textbf{Go} and \textbf{React}.
\end{itemize}
\hfill \break
}}
{\footnotesize{\textbf{MagusVR | 2019} (http://bit.ly/MagusVR)}}
{\footnotesize{
\newline\textbf{Role:} Project Lead, Software Engineer
% \newline\textbf{Fantasy Role-Playing Virtual Reality Game}
\begin{itemize}
	\item[--] Crafted a Virtual Reality game in \textbf{Unity} and \textbf{C\#} to play a role as a magician, but with a twist of utilizing only physical hand gestures.
\end{itemize}
\hfill \break
}}
{\footnotesize{\textbf{UpCrate | 2018} (http://bit.ly/UpCrate)}}
{\footnotesize{
\newline\textbf{Role:} Project Lead, Software Engineer
% \newline\textbf{Laravel File-Sharing Web Application Hosted On AWS EC2}
\begin{itemize}
	\item[--] Deployed and developed a \textbf{Laravel} web app to demonstrate \textbf{SQLite3} integration of a file-sharing schema among multiple users onto an \textbf{AWS EC2}.
\end{itemize}
\hfill \break
}}
{\footnotesize{\textbf{Reality Stocks | 2018} (http://bit.ly/Reality-Stocks)}}
{\footnotesize{
\newline\textbf{Role:} Project Lead, Software Engineer
% \newline\textbf{Financial Stock Navigation Using Only Hand Gestures}
\begin{itemize}
	\item[--] Designed a \textbf{React} web app to allow hand gestures to navigate through financial stocks using the Leap Motion Hardware SDK.
\end{itemize}
}}
\hfill \break
%{\footnotesize{\textbf{Embedded Helicopter | 2018} (http://bit.ly/Embed-Heli)}}
%{\footnotesize{
% \newline\textbf{Role:} Software \& Hardware Engineer
%\newline\textbf{Flying A Helicopter With A Microcontroller}
%\begin{itemize}
%	\item[--] Designed a C-based multitasking operating system to make a helicopter fly up an down.
%\end{itemize}
%}}
%\hfill \break
{\footnotesize{\textbf{AITAR | 2017} (http://bit.ly/ait-ar)}}
{\footnotesize{
\newline\textbf{Role:} Project Lead, Android Software Developer
% \newline\textbf{Augmented Reality Fantasy Multiplayer Android Game}
\begin{itemize}
	\item[--] Used Vuforia AR SDK, \textbf{Firebase}, Fragments, \textbf{OpenGL} to superimpose a health bar onto our world to play attack the player using \textbf{Android}.
\end{itemize} 
}}
\hfill \break
% {\footnotesize{\textbf{DefCom | 2017} (http://bit.ly/DefComCrypto)}}
% {\footnotesize{
\newline\textbf{Role:} Project Lead, Software Engineer
% \newline\textbf{Secure Multi-Party Chat Application}
% \begin{itemize}
% 	\item[--] Interfaces with PyCrypto and Tornado Web Framework maximizing Python integration with newly designed cryptographic primitives and protocols.
% \end{itemize} 
% }}
% \hfill \break
{\footnotesize{\textbf{Packaged Life | 2017} (Non-Disclosure Agreement)}}
{\footnotesize{
\newline\textbf{Role:} Chief Technology Officer
% \newline\textbf{Educational Email Prototyping Solution}
\begin{itemize}
	\item[--] Integrated a mass email mechanism into \textbf{Python-Flask} ecosystem using AWS technologies, such as: \textbf{EC2}, \textbf{Elastic Beanstalk}, \textbf{Route53}, \textbf{DynamoDB}, \textbf{S3}, \textbf{Lambda}, \textbf{SES} into product backbone to scale 500+ users.
\end{itemize} 
}}
%\hfill \break
\section*{\underline{Education}}
{\footnotesize{
\textbf{University of Puget Sound} (Tacoma, WA, USA)
\newline B.S. in \textbf{Computer Science}
\newline May 2019
\newline\newline\textbf{Awards \& Honors}
\begin{itemize}
	\item[--] National Department of Defense SMART Scholarship
	\item[--] Horatio Alger Scholarship
	\item[--] Washington State Opportunity Scholarship
	\item[--] Benjamin A. Gilman International Scholarship   
\end{itemize} 
% \newline\newline\textbf{Certificates}
% \begin{itemize}
	% \item[--] AWS Developer (On-Track: \textbf{11/2020})
% \end{itemize} 
}}

\hfill  \quad

\end{multicols} 

\end{document}